Appendix A: Code and supplementary figures for simulation and policy analyis

### 2018-01-29 appendix/appendixB.Rmd
update appendix with clean names, a bit more text

```{r aethetics, include=FALSE}
#library(printr)
knitr::opts_chunk$set(message=FALSE, comment="", cache=TRUE)
```

@@

extrafont::loadfonts()
knitr::opts_chunk$set( dev="cairo_pdf")
hrbrthemes::import_roboto_condensed() 
ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())
#palette <- ptol_pal()(6)
```

```{r}
palette <- c("#D9661F", "#3B7EA1",  "#6C3302", "#FDB515", "#00B0DA",  "#CFDD45") # berkeley colors
colors <- set_names(c(palette[c(1:4,2,5)], "grey", "black"), 
                    c("TAC", "POMDP", "MSY", "CE", 
                      "POMDP: low prior",
                      "POMDP: medium prior",
                      "biomass",
                      "catch"))
```

>>>>

```{r knitr, include=FALSE}
knitr::opts_chunk$set(comment="", message=FALSE, cache=TRUE, dev="cairo_pdf")
```

@@

extrafont::loadfonts()
hrbrthemes::import_roboto_condensed() 
ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())

palette <- c("#D9661F", "#3B7EA1", "#6C3302",
             "#FDB515", "#00B0DA",  "#CFDD45")
colors <- set_names(c(palette[c(1:4,2,5)], "grey", "black"), 
                    c("TAC", "POMDP", "MSY", "CE", 
                      "POMDP: low prior",
                      "POMDP: medium prior",
                      "biomass",
                      "catch"))
scale_colour_discrete <- function(...) scale_colour_manual(..., values=colors)
scale_fill_discrete <- function(...) scale_fill_manual(..., values=colors)
```

### 2018-01-29 appendix/appendix_harvestfirst.Rmd
update appendix with clean names, a bit more text

---
title: "Appendix A: Code and supplementary figures for simulation and policy analyis"
author: "Carl Boettiger"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r aethetics, include=FALSE}
knitr::opts_chunk$set(comment="", message=FALSE, cache=TRUE)
```

@@

extrafont::loadfonts()
knitr::opts_chunk$set( dev="cairo_pdf")
hrbrthemes::import_roboto_condensed() 
ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())
```

```{r colors}
#palette <- ptol_pal()(6)
palette <- c("#D9661F", "#3B7EA1",  "#6C3302", "#FDB515", "#00B0DA",  "#CFDD45")
colors <- set_names(c(palette[c(1:4,2,5)], "grey", "black"), 
                    c("TAC", "POMDP", "MSY", "CE", 
                      "POMDP: low prior",
                      "POMDP: high prior",
                      "biomass",
                      "catch"))
```

@@

## Basic deterministic model

@@

## Unlike classic Graham-Schaefer, this assumes harvest occurs right after assessment, before recruitment
f <- function(x, h){ 
    s <- pmax(x-h, 0) 
    s + s * r * (1 - s / K) 
}
```

@@

## Calculating MSY

@@

```{r}
#B_MSY <- S_star     # recruit first, as in classic Graham-Schaefer
B_MSY <- f(S_star,0) # harvest first, we observe the population at B_msy + h

@@

F_MSY <- MSY / B_MSY  
F_PGY = 0.8 * F_MSY
```

@@

msy_policy <- function(x) F_MSY * x
pgy_policy <- function(x) F_PGY * x

@@

    for(t in 1:(Tmax-1)){
      action[t] <- policy(state[t])
      obs[t] <- state[t] - action[t]  # if we observe after harvest but before recruitment
      state[t+1] <- f(state[t], action[t]) 
    }
    data.frame(time = 1:Tmax, state, action, obs)
  }

det_sims <- 
  list(msy = msy_policy, 
       pgy = pgy_policy,
       det = escapement_policy) %>% 
  map_df(do_det_sim, 
         f, x0, Tmax, 
         .id = "method")

@@

With no stochasticity, MSY leads to the same long-term stock size as under the constant escapement rule, but takes longer to get there.  This level is essentially $B_{MSY}$, though because the model considered here implements events in the order: *observe, harvest, recruit*; rather than *observe, recruit, harvest*, we see the stock at the pre-harvest size of $B_{MSY} + H_{MSY}$ (that is, $K/2 + rK/4$).   More conservative rules, such as a harvest set to 80% of MSY result in faster recovery of the stock than under MSY, but slower than under constant escapement.  Due to the reduced maximum harvest rate, such rules lead to stock returning to a value higher than $B_${MSY}$.

```{r fig.width=3.5, fig.height=3.5}
det_sims %>%
  mutate(method = fct_recode(method, 
                             "CE" = "det",
                             "TAC" = "pgy",
                             "MSY" = "msy")) %>%
  ggplot(aes(time, state, col=method)) + 
  geom_line(lwd=1) + 
  scale_color_manual(values = colors) +
  coord_cartesian(ylim = c(0, 1)) + 
  theme(legend.position = "bottom") + 
  ylab("Mean biomass")
```

@@

##  Introduce a discrete grid

@@

policies <- data.frame(
#  det = index(pmax(f(states,0) - S_star,0), actions), # obs,recruit,harv, f(x_t) - h_t
  det = index(escapement_policy(states),     actions), # obs,harv,recruit, f(x_t - h_t)
  msy = index(msy_policy(states),               actions),
  pgy = index(pgy_policy(states),               actions))
```

@@

We compute POMDP matrices for a range of `sigma_g` and `sigma_m` values:

@@

```{r eval=FALSE}
dir.create(log_dir)

## POMDP solution 
## (slow, >10,000 seconds per scenario for discount ~ 0.95;
## needs much longer for discount ~ 0.99)
system.time(
  alphas <- 
    parallel::mclapply(1:length(models), 
    function(i){
      log_data <- data.frame(model = "gs", 
                             r = r, 
                             K = K, 
                             sigma_g = meta[i,"sigma_g"][[1]], 
                             sigma_m = meta[i,"sigma_m"][[1]], 
                             noise = "normal",
                             scenario = meta[i, "scenario"][[1]])

@@

@@

unif_prior <- rep(1, length(states)) / length(states)
pomdp_sims <- 
  map2_dfr(models, alphas, function(.x, .y){
             sim_pomdp(.x$transition, .x$observation, .x$reward, discount, 
                       unif_prior, x0 = x0, Tmax = Tmax, alpha = .y,
                       reps = reps)$df %>% 
              mutate(method = "pomdp") # include a column labeling method
           },
           .id = "scenario")
```

Combine the resulting data frames

@@

sim_col_types <- paste0(gsub("^(\\w).*", "\\1", sapply(unname(sims), class)), collapse = "")
write_csv(sims, file.path(log_dir, "sims.csv"))
```

@@

We the results varying over different noise intensities, sigma_g, and sigma_m.  Figure 1 of the main text considers the case of sigma_g = 0.05, sigma_m = 0.1

```{r}
sim_col_types <-  "inicnnn"
sims <- read_csv(file.path(log_dir, "sims.csv"), col_types = sim_col_types)

@@

##  Figure S3

Economic Value

```{r}
sims %>%
  select(time, value, rep, method, sigma_m, sigma_g) %>%
  filter(sigma_g %in% c("0.1", "0.15")) %>%
  group_by(rep, method, sigma_m, sigma_g) %>%
  summarise(npv = sum(value)) %>%  
  group_by(method, sigma_m, sigma_g) %>%
  summarise(net_value = mean(npv), se = sd(npv) / mean(npv)) %>%
  ungroup() %>%
  mutate(method = fct_recode(method,
                             "MSY" = "msy",
                             "CE" = "det",
                             "TAC" = "pgy",
                             "POMDP" = "pomdp")) %>%

  ggplot(aes(method, net_value, ymin=net_value-se, ymax=net_value+se, fill=method)) + 
  geom_bar(position=position_dodge(), stat="identity") + 
  geom_errorbar(size=.3,width=.2,
                position=position_dodge(.9)) +
  facet_grid(sigma_m~sigma_g, 
             labeller = label_bquote(sigma[m] == .(sigma_m),
                                     sigma[g] == .(sigma_g))) +
  theme(legend.position = "none") + 
  scale_color_manual(values = colors) +
  scale_fill_manual(values = colors) +
  ylab("expected net present value")

@@

-----

@@

While the POMDP approach requires an estimate of the measurement error, the precise distribution of measurement errors will itself be unknown in most cases.  However, the POMDP approach is quite robust to overestimation of the measurement error.  As an extreme example of this, we consider the case where the POMDP solution assumes the largest measurement error level considered here, $\sigma_m = 0.15$, while performing simulations in which measurements occur without error. In such a scenario, the

```{r overest}
set.seed(12345)
true <- 3 # sigma_g = 0.15, sigma_m = 0
source("../appendix/pomdp_overestimate.R")
pomdp_overest_sims <- 
  map2_dfr(models, alphas, function(.x, .y){
    pomdp_overestimates(transition = .x$transition, 
            model_observation = .x$observation, 
            reward = .x$reward, 
            discount = discount, 
            true_observation = models[[true]]$observation,
            x0 = x0,
            Tmax = Tmax,
            alpha = .y,
            reps = reps)$df %>% 
              mutate(method = "pomdp") # include a column labeling method
           },
           .id = "scenario"
  )
```

Combine the resulting data frames

@@

overest %>% filter(method != "pomdp", sigma_m == "0")  %>%
  bind_rows(
  overest %>% filter(method == "pomdp", sigma_m == "0.15")) %>%
  select(-sigma_m, -sigma_g) %>%
  mutate(method = fct_recode(method,
                             "MSY" = "msy",
                             "CE" = "det",
                             "TAC" = "pgy",
                             "POMDP" = "pomdp")) %>%
  write_csv(file.path(log_dir, "overest_sims.csv"))
```

@@

## Policy plots

@@

Note that when recruitment occurs before harvest, $f(x) - h$, to get to $X_t = B_{MSY}$ as fast as possible, we actually want to harvest a little bit when X is below $B_{MSY}$, so that rather than over-shooting $B_{MSY}$ (deterministic) recruitment would land us right at it $B_{MSY}$.  This corresponds to constant escapement.  The discrete grid makes these appear slightly stepped.

Note that the deterministic solution crosses the MSY solution at an observed value of $B_{MSY}$ (i.e. $K/2 = 0.5$).  PGY harvests are always smaller than MSY harvests, but unlike the deterministic optimal solution, PGY and MSY solutions never go to zero.

```{r}
policy_table %>% 
  ggplot(aes(state, harvest, col=policy)) + 
  geom_line()  + 
  coord_cartesian(xlim = c(0,K), ylim = c(0, .8))
```

Note that when recruitment happens before harvest, escapement is $f(x_t) - h_t$, not $x_t - h_t$.  The effect of a continuous function map $f$ on a discrete grid is also visible as slight wiggles when we plot in terms of escapement instead of harvest (as is common in the optimal control literature in fisheries, e.g. @Sethi2005).

Note that under the optimal solution, escapement is effectively constant at $B_{MSY} = 0.5$: for all states above a certain size the population
is harvested back down to that size. Note that even stocks observed at states slightly below $B_{MSY} = 0.5$ achieve this target escapement, since we are following the classic Graham Shaeffer formulation here where we observe first, then recruitment happens before harvest, and thus we see the population at smaller size than we harvest it.  In classical escapement analysis, observations are usually indexed instead to occur immediately before harvests, and this inflection point occurs right at $B_{MSY}$.

```{r}
policy_table   %>% 
  ggplot(aes(state, escapement, col=policy)) + 
  geom_line() + 
  coord_cartesian(xlim = c(0,K), ylim = c(0, .8))

### Policies under uncertainty

In strategies whose policies are shown in the above plots all ignore both stochasticity and measurement error.  If want to compare these to an MDP or POMDP policy, we must specify the level of uncertainty.

In the absence of measurement uncertainty this is straight forward.  @Reed1979 essentially tells us that for small growth noise (satisfying or approximately satisfying Reed's self-sustaining condition) that the stochastic optimal policy is equal to the deterministic optimal policy.  We can confirm this numerically as follows.

First we grab the transition matrix we have already defined for small `sigma_g`:

```{r}
i <- meta %>% filter(sigma_g == 0.02, sigma_m ==0) %>% pull(scenario) %>% as.integer()
m <- models[[i]]
```

With no observation uncertainty, we can solve numerically for the optimal policy with stochastic dynamic programming

```{r}
mdp <- MDPtoolbox::mdp_policy_iteration(m$transition, m$reward, discount) 
```

Adding this to the plot we see the result is identical to the deterministic case:

```{r}
bind_rows(policy_table,
  data.frame(state = states, 
             policy = "sdp 0.02",
             harvest = actions[mdp$policy],
             stringsAsFactors = FALSE) %>%
  mutate(escapement = state- harvest)) %>% 
  ggplot(aes(state, harvest, col=policy)) + 
  geom_line()  + 
  coord_cartesian(xlim = c(0,K), ylim = c(0, .8))
```

Repeating this for larger stochasticity, we get a slightly more conservative result:

```{r}
i <- meta %>% filter(sigma_g == 0.15, sigma_m ==0) %>% pull(scenario) %>% as.integer()
m <- models[[i]]
mdp <- MDPtoolbox::mdp_policy_iteration(m$transition, m$reward, discount) 
```

```{r}
bind_rows(policy_table,
  data.frame(state = states, 
             policy = "sdp 0.15",
             harvest = actions[mdp$policy],
             stringsAsFactors = FALSE)) %>% 
  ggplot(aes(state, harvest, col=policy)) + 
  geom_line()  + 
  coord_cartesian(xlim = c(0,K), ylim = c(0, .8))
```

@@

```{r}
i <- meta %>% filter(sigma_g == 0.15, sigma_m ==0.1) %>% pull(scenario) %>% as.integer()
m <- models[[i]]
alpha <- alphas[[i]] # we need the corresponding alpha vectors  
```

@@

For more realistic set of priors, we will consider priors centered at the target $B_{MSY}$ size (or $S^*$ in the language of Reed), at half $B_{MSY}$, and at 1.5 times $B_{MSY}$, each with a standard deviation of $\sigma_m = 0.1$ (i.e. the uncertainty around a single observation of a stock at that size.)

```{r}
i_star <- which.min(abs(states - S_star))
i_low <- which.min(abs(states - 0.25 * K))
i_high <- which.min(abs(states - 0.75 * K))

prior_star <- m$observation[,i_star,1]
prior_low <- m$observation[,i_low,1]
prior_high <- m$observation[,i_high,1]

@@

all_policies <- bind_rows(policy_table, pomdp_policies)

write_csv(all_policies, file.path(log_dir, "all_policies.csv"))
```

POMDP policies depend on the prior belief.

```{r fig.width=5, fig.height=7, fig.cap=""}
priors <- 
  data_frame(states, 
             prior_low,
             prior_star,
             unif_prior,
             prior_high) %>%
  select(state = states, 
         "POMDP: low prior" = prior_low, 
         "POMDP: high prior" = prior_high) %>%
  gather(policy, prior, -state) %>%
  mutate(prior = prior*10)

policy_df <- all_policies %>% 
  filter(policy %in% c("low", "high", "det", "pgy")) %>%
  mutate(policy = fct_recode(policy,
                             "CE" = "det",
                             "TAC" = "pgy",
                             "POMDP: low prior" = "low",
                             "POMDP: high prior" = "high"
                             ))

policies_w_priors <- right_join(priors, policy_df, by = c("state", "policy"))

@@

```{r fig.width=5, fig.height=7, fig.cap=""}
policies_w_priors %>% 
  gather(panel, value, -state, -policy) %>%
  ggplot(aes(state, value, col=policy)) + 
  geom_line(lwd=1)  +
  facet_wrap(~panel, ncol=1, scales = "free_y") +
  scale_color_manual(values = colors) +
  coord_cartesian(xlim = c(0,1), ylim = c(0,.8)) + 
  theme(legend.position = "bottom")
```

>>>>

---
title: "Appendix A: Code and supplementary figures for simulation and policy analyis"
author: "Carl Boettiger"
date: "`r Sys.Date()`"
output: pdf_document
bibliography: ../manuscripts/citations.bib

---

# Overview

1. Model definition:
2. Deterministic Solutions
3. Discretization and the POMDP solution
4. Simulation

```{r knitr, include=FALSE}
knitr::opts_chunk$set(comment="", message=FALSE, warning = FALSE, cache=TRUE, dev="cairo_pdf")
```

@@

extrafont::loadfonts()
hrbrthemes::import_roboto_condensed() 
ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())

## Set colors
#palette <- ptol_pal()(6)
palette <- c("#D9661F", "#3B7EA1",  "#6C3302", "#FDB515", "#00B0DA",  "#CFDD45")
colors <- set_names(c(palette[c(1:4,2,5)], "grey", "black", palette[6]), 
                    c("TAC", "POMDP", "MSY", "CE", 
                      "POMDP: low prior",
                      "POMDP: high prior",
                      "biomass",
                      "catch",
                      "SDP"))
## Set as default palette so we can omit scale_color_manual in every plot call
## https://stackoverflow.com/a/44307181/258662
scale_colour_discrete <- function(...) scale_colour_manual(..., values=colors)
scale_fill_discrete <- function(...) scale_fill_manual(..., values=colors)
```

@@

# Basic deterministic model

@@

## Unlike classic Graham-Schaefer, this assumes harvest 
## occurs right after assessment, before recruitment
f <- function(x, h){ 
    s <- pmax(x-h, 0) 
    s + s * r * (1 - s / K) 
}
```

@@

# Calculating MSY & TAC

@@

```{r}
#B_MSY <- S_star     # recruit first, as in classic Graham-Schaefer
B_MSY <- f(S_star,0) # harvest first, we observe the population at B_MSY + h

@@

F_MSY <- MSY / B_MSY  
F_TAC = 0.8 * F_MSY
```

@@

```{r}
MSY_policy <- function(x) F_MSY * x
TAC_policy <- function(x) F_TAC * x

@@

    for(t in 1:(Tmax-1)){
      action[t] <- policy(state[t])
      obs[t] <- state[t] - action[t]  # we observe->harvest->recruitment
      state[t+1] <- f(state[t], action[t]) 
    }
    data.frame(time = 1:Tmax, state, action, obs)
  }

det_sims <- 
  list(MSY = MSY_policy, 
       TAC = TAC_policy,
       CE = escapement_policy) %>% 
  map_df(do_det_sim, 
         f, x0, Tmax, 
         .id = "method")

@@

With no stochasticity, MSY leads to the same long-term stock size as under the constant escapement rule, but takes longer to get there.  This level is essentially $B_{MSY}$, though because the model considered here implements events in the order: *observe, harvest, recruit*; rather than *observe, recruit, harvest*, we see the stock at the pre-harvest size of $B_{MSY} + H_{MSY}$ (that is, $K/2 + rK/4$).   More conservative rules, such as a harvest set to 80% of MSY result in faster recovery of the stock than under MSY, but slower than under constant escapement.  Due to the reduced maximum harvest rate, such rules lead to stock returning to a value higher than $B_{MSY}$.

```{r fig.width=5, fig.height=5}
det_sims %>%
  ggplot(aes(time, state, col=method)) + 
  geom_line(lwd=1) + 
  coord_cartesian(ylim = c(0, 1)) + 
  theme(legend.position = "bottom") + 
  ylab("Mean biomass")
```

@@

#  Introduce a discrete grid

@@

policies <- data.frame(
#  CE = index(pmax(f(states,0) - S_star,0), actions), # obs,recruit,harv, f(x_t) - h_t
  CE = index(escapement_policy(states),     actions), # obs,harv,recruit, f(x_t - h_t)
  MSY = index(MSY_policy(states),               actions),
  TAC = index(TAC_policy(states),               actions))
```

@@

We compute POMDP matrices for a range of `sigma_g` and `sigma_m` values.  (We consider `sigma_g = 0.02` rather than precisely zero here to avoid a degeneracy in the discretized tranisition matrix. Calculations for the precise deterministic solution can be solved without discretization as shown above, and match the results of this nearly-zero nosie level in the discrete simulation, as expected.)

@@

```{r eval=FALSE}
dir.create(log_dir)
system.time(
  alphas <- 
    parallel::mclapply(1:length(models), 
    function(i){
      log_data <- data.frame(model = "gs", 
                             r = r, 
                             K = K, 
                             sigma_g = meta[i,"sigma_g"][[1]], 
                             sigma_m = meta[i,"sigma_m"][[1]], 
                             noise = "normal",
                             scenario = meta[i, "scenario"][[1]])

@@

------

# Simulations

Having calculated the POMDP solution in terms of these `alpha` vectors, we can easily compute the POMDP policy for any given prior and update the prior given further observations according to Bayes rule.  We assume a uniform prior belief at the start of the POMDP simulation.  These tasks are perfromed by the `sim_pomdp` fucntion. Simulating the static strategies (CE, MSY, TAC) is easier, since the policy is uniquely determined by the observed state; we simply need to simulate the stochastic growth and process and measurement with error at each time step an then compute the corrsponding policy. The `sim_pomdp` function performs such static simulations when given a pre-specified policy instead of a set of `alpha` vectors.

@@

unif_prior <- rep(1, length(states)) / length(states)
pomdp_sims <- 
  map2_dfr(models, alphas, function(.x, .y){
             sim_pomdp(.x$transition, .x$observation, .x$reward, discount, 
                       unif_prior, x0 = x0, Tmax = Tmax, alpha = .y,
                       reps = reps)$df %>% 
              mutate(method = "POMDP") # include a column labeling method
           },
           .id = "scenario")
```

We then combine the resulting data frames, transition (mutate) the units from grid indices (`state`, `action` $\in 1 ... N$) to continuous values (`states`, `actions` $\in [0,2]$), and select necessary columns before writing the data out to a file.

@@

write_csv(sims, file.path(log_dir, "sims.csv"))
```

@@

We the results varying over different noise intensities, `sigma_g`, and `sigma_m`.  Note that Figure 1 of the main text shows only the case of `sigma_g = 0.15`, `sigma_m = 0.1` and omits MSY to simplify the presentation.

```{r}
sims <- read_csv(file.path(log_dir, "sims.csv"), col_types = "inicnnn")

@@

##  Figure S3: Economic value

Economic value is shown under varying noise levels under each strategy.

```{r}
sims %>%
  select(time, value, rep, method, sigma_m, sigma_g) %>%
  filter(sigma_g %in% c("0.1", "0.15")) %>%
  group_by(rep, method, sigma_m, sigma_g) %>%
  summarise(npv = sum(value)) %>%  
  group_by(method, sigma_m, sigma_g) %>%
  summarise(net_value = mean(npv), se = sd(npv) / mean(npv)) %>%
  ungroup() %>%

  ggplot(aes(method, net_value, ymin=net_value-se, ymax=net_value+se, fill=method)) + 
  geom_bar(position=position_dodge(), stat="identity") + 
  geom_errorbar(size=.3,width=.2,
                position=position_dodge(.9)) +
  facet_grid(sigma_m~sigma_g, 
             labeller = label_bquote(sigma[m] == .(sigma_m),
                                     sigma[g] == .(sigma_g))) +
  theme(legend.position = "none") + 
  ylab("expected net present value")

@@

@@

While the POMDP approach requires an estimate of the measurement error, the precise distribution of measurement errors will itself be unknown in most cases.  However, the POMDP approach is quite robust to overestimation of the measurement error.  As an extreme example of this, we consider the case where the POMDP solution assumes the largest measurement error level considered here, $\sigma_m = 0.15$, while performing simulations in which measurements occur without error:

```{r overest}
set.seed(12345)
true <- 3 # sigma_g = 0.15, sigma_m = 0
source("../appendix/pomdp_overestimate.R")
pomdp_overest_sims <- 
  map2_dfr(models, alphas, function(.x, .y){
    pomdp_overestimates(transition = .x$transition, 
            model_observation = .x$observation, 
            reward = .x$reward, 
            discount = discount, 
            true_observation = models[[true]]$observation,
            x0 = x0,
            Tmax = Tmax,
            alpha = .y,
            reps = reps)$df %>% 
              mutate(method = "POMDP") # include a column labeling method
           },
           .id = "scenario"
  )
```

Combine the POMDP simulations results from over-estimating measurement error with the previous results from the static policies for comparison:

@@

overest %>% filter(method != "POMDP", sigma_m == "0")  %>%
  bind_rows(
  overest %>% filter(method == "POMDP", sigma_m == "0.15")) %>%
  select(-sigma_m, -sigma_g) %>%

  write_csv(file.path(log_dir, "overest_sims.csv"))
```

@@

--------

# Policy plots

@@

Note that when recruitment occurs before harvest, $f(x) - h$, to get to $X_t = B_{MSY}$ as fast as possible, we actually want to harvest a little bit when X is below $B_{MSY}$, so that rather than over-shooting $B_{MSY}$ (CEerministic) recruitment would land us right at it $B_{MSY}$.  This corresponds to constant escapement.  The discrete grid makes these appear slightly stepped.

Note that the deterministic solution crosses the MSY solution at an observed value of $B_{MSY}$ (i.e. $K/2 = 0.5$).  TAC harvests are always smaller than MSY harvests, but unlike the deterministic optimal solution, TAC and MSY solutions never go to zero.

```{r fig.width = 5, fig.height=7}
h_plot <- policy_table %>% 
  ggplot(aes(state, harvest, col=policy)) + 
  geom_line(lwd=1)  + 
  coord_cartesian(xlim = c(0,K), ylim = c(0, .8))  +
  theme(legend.position = "none")

e_plot <- policy_table   %>% 
  ggplot(aes(state, escapement, col=policy)) + 
  geom_line(lwd=1) + 
  coord_cartesian(xlim = c(0,K), ylim = c(0, .8)) +
  theme(legend.position = "bottom")

gridExtra::grid.arrange(h_plot, e_plot, layout_matrix = rbind(1,2))
```

When recruitment happens before harvest, escapement is $f(x_t) - h_t$, not $x_t - h_t$.  The effect of a continuous function map $f$ on a discrete grid is also visible as slight wiggles when we plot in terms of escapement instead of harvest (as is common in the optimal control literature in fisheries, e.g. @Sethi2005).

Under the optimal solution, escapement is effectively constant at $B_{MSY} = 0.5$: for all states above a certain size the population is harvested back down to that size. Note that even stocks observed at states slightly below $B_{MSY} = 0.5$ achieve this target escapement, since we are following the classic Graham Shaeffer formulation here where we observe first, then recruitment happens before harvest, and thus we see the population at smaller size than we harvest it.  In classical escapement analysis, observations are usually indexed instead to occur immediately before harvests, and this inflection point occurs right at $B_{MSY}$.

### Policies under uncertainty: S = D

In strategies whose policies are shown in the above plots all ignore both stochasticity and measurement error.  If want to compare these to an MDP or POMDP policy, we must specify the level of uncertainty. In the absence of measurement uncertainty this is straight forward.  @Reed1979 essentially tells us that for small growth noise (satisfying or approximately satisfying Reed's self-sustaining condition) that the stochastic optimal policy is equal to the deterministic optimal policy.  We can confirm this numerically as follows.

First we grab the transition matrix we have already defined when `sigma_g = 0.1`, and then solve the Stochastic Dynamic Programming solution (SDP) for the (fully observed) Markov Decision Process (MDP) using the `MDPtoolbox` package:

```{r}
i <- meta %>% filter(sigma_g == 0.1, sigma_m ==0) %>%
  pull(scenario) %>% as.integer()
m <- models[[i]]
mdp <- MDPtoolbox::mdp_policy_iteration(m$transition, m$reward, discount) 
```

We plot the resulting policy in comparison with the other static policies, which shows that even for such a large noise we get a stochastic constant escapement equal to that of of the deterministic CE calculation:

```{r}
bind_rows(policy_table,
  data_frame(state = states, 
             policy = "SDP",
             harvest = actions[mdp$policy],
             escapement = states - actions[mdp$policy])) %>% 
  ggplot(aes(state, escapement, col=policy)) + 
  geom_line(lwd=1)  + 
  coord_cartesian(xlim = c(0,K), ylim = c(0, .8)) + 
  labs(caption = "SDP solution when sigma_g = 0.1")
```

Repeating this larger stochastic growth `sigma_g = 0.15`, shows only slight deviation from CE ($S > D$, as @Reed1979 proves for sufficiently large noise to violate the self-sustaining criterion.  Technically since our noise model in normally distributed none of our populations are self-sustaining for infinite time, but as these simulations show, in practice that deviation is very small.)

```{r}
i <- meta %>% filter(sigma_g == 0.15, sigma_m ==0) %>%
  pull(scenario) %>% as.integer()
m <- models[[i]]
mdp <- MDPtoolbox::mdp_policy_iteration(m$transition, m$reward, discount)

bind_rows(policy_table,
  data_frame(state = states, 
             policy = "SDP",
             harvest = actions[mdp$policy],
             escapement = states - actions[mdp$policy])) %>% 
  ggplot(aes(state, escapement, col=policy)) + 
  geom_line(lwd=1)  + 
  coord_cartesian(xlim = c(0,K), ylim = c(0, .8)) + 
  labs(caption = "SDP solution when sigma_g = 0.15")
```

@@

```{r}
i <- meta %>% 
  filter(sigma_g == 0.15, sigma_m == 0.1) %>% 
  pull(scenario) %>% as.integer()
m <- models[[i]]
alpha <- alphas[[i]] # we need the corresponding alpha vectors  
```

@@

For more realistic set of priors, we will consider priors centered at the target $B_{MSY}$ size (or $S^*$ in the language of Reed), at half $B_{MSY}$ (i.e. $K/4$), and at $\tfrac{3}{4} K$, each with a standard deviation of $\sigma_m = 0.1$ (i.e. the uncertainty around a single observation of a stock at that size.)

```{r}
prior_star <- m$observation[, which.min(abs(states - S_star)),1]
prior_low <- m$observation[,which.min(abs(states - 0.25 * K)),1]
prior_high <- m$observation[,which.min(abs(states - 0.75 * K)),1]

@@

all_policies <- bind_rows(policy_table, pomdp_policies)
write_csv(all_policies, file.path(log_dir, "all_policies.csv"))
```

Plot these policies in terms of both Harvest and Escapement:

```{r}
recode_policies <- 
  all_policies %>%
  filter(policy %in% c("CE", "MSY", "TAC", "low", "high")) %>%
  mutate(policy = 
    fct_recode(policy, 
               "POMDP: low prior" = "low", 
               "POMDP: high prior" = "high"))
```

```{r}
recode_policies %>%
  ggplot(aes(state, escapement, col = policy)) + 
  geom_line(lwd=1) + 
  coord_cartesian(xlim = c(0,1), ylim=c(0,.8))
```

```{r}
recode_policies %>%
  ggplot(aes(state, harvest, col = policy)) + 
  geom_line(lwd=1) + 
  coord_cartesian(xlim = c(0,1), ylim=c(0,.6))
```

```{r, include=FALSE}
## Data for manuscript; combine prior distribution data with policy data
priors <- 
  data_frame(states, 
             prior_low,
             prior_star,
             unif_prior,
             prior_high) %>%
  select(state = states, 
         "POMDP: low prior" = prior_low, 
         "POMDP: high prior" = prior_high) %>%
  gather(policy, prior, -state) %>%
  mutate(prior = prior*10)
write_csv(priors, file.path(log_dir, "priors.csv"))
```

```{r}
p3 <- read_csv(file.path(log_dir, "priors.csv")) %>%
ggplot(aes(state, prior, col = policy)) + 
  geom_line(lwd=1) +
  coord_cartesian(xlim = c(0,1))
p3
```

```{r include = FALSE}
policy_df <- all_policies %>% 
  filter(policy %in% c("low", "high", "CE", "TAC")) %>%
  mutate(policy = fct_recode(policy,
                             "POMDP: low prior" = "low",
                             "POMDP: high prior" = "high"
                             )) 
policies_w_priors <- right_join(priors, policy_df, by = c("state", "policy"))

@@

```{r fig.width=5, fig.height=7, include = FALSE}
policies_w_priors %>% 
  gather(panel, value, -state, -policy) %>%
  ggplot(aes(state, value, col=policy)) + 
  geom_line(lwd=1)  +
  facet_wrap(~panel, ncol=1, scales = "free_y") +
  coord_cartesian(xlim = c(0,1), ylim = c(0,.8)) + 
  theme(legend.position = "bottom")
```
